---
title: "COMPSCIX 415.2 Homework 1"
author: "Aline Hankey"
date: "6/11/2018"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
My Github repository for my assignments can be found at **this URL**: https://github.com/alinemariee/compscix-415-2-assignments

```{r load_packages, warning=FALSE, message=FALSE}
library(mdsr)
library(tidyverse)
data("WorldCities")
```
**Question 1:**


This data set includes 23,018 observations and 10 variables. Some of the variable names include: (city) name, country, and population. 
```{r echo=FALSE}
glimpse(WorldCities)
WorldCities <- head(WorldCities, 200) # 200 rows
country_col <- WorldCities$country
unique(country_col)
## [1] "AD" "AE" "AF" "AG" "AI" "AL" "AM" "AO" "AR"
region_col <- WorldCities$region
unique(region_col)
```
**Question 2:**

Above you'll see the unique country regions.

**Question 3, Part A:**

Below, you'll see unique countries.
```{r echo=FALSE}
WorldCities %>% select(country) %>% unique()
```
**Question 3, Part B:**


Question Three, Part B (**below**) features a plot examining population by city.
```{r echo=FALSE}
WorldCities %>% ggplot(aes(x = population)) + geom_histogram(binwidth = 1e6) + xlab ('City Population') 
binwidth= (15)
```

**Question 4:**


In Question 4, you'll see a tweaked version of the same plot, with updates to theme.
```{r echo=FALSE, tidy=TRUE}
WorldCities %>% ggplot(aes(x = population)) + geom_histogram(binwidth = 1e6) + xlab ('City Population') + ylab('Number of Cities') + theme_bw(base_size = 12) + theme_light() + ggtitle('City Population Breakdown')
```



